canaper: Categorical analysis of neo- and paleo-endemism in R

### 2022-08-31 ms/ms.Qmd
Refactor to use quarto

---
title: "canaper: Categorical analysis of neo- and paleo-endemism in R"
author: "Joel Nitta"
date: "10/27/2021"
output: html_document
bibliography: references.yaml
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r cpr-rand-comm-demo}
data(phylocom)

@@

```{r cpr-rand-comm-demo}
rand_test_results <- cpr_rand_test(
  phylocom$comm, phylocom$phy, null_model = "curveball")

@@

```{r cpr-classify-endem-demo}
canape_results <- cpr_classify_endem(rand_test_results)

@@

```{r cpr-rand-comm-parallel-demo}
library(future)

@@

```{r acacia-demo}
library(future)
library(canaper)

@@

```{r acacia-plot}
library(patchwork) # for multipart-panels
library(tidyverse) # includes ggplot2, other packages for data tidying

@@

@@

>>>>

---
title: "canaper: Categorical analysis of neo- and paleo-endemism in R"
bibliography: references.yaml
csl: methods-in-ecology-and-evolution.csl
format:
  docx:
    toc: false
    number-sections: false
    highlight-style: github
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
#| label: cpr-rand-comm-demo
library(canaper)

data(phylocom)

@@

```{r}
#| label: cpr-rand-test-demo
rand_test_results <- cpr_rand_test(
  phylocom$comm, phylocom$phy, null_model = "curveball")

@@

```{r}
#| label: cpr-classify-endem-demo
canape_results <- cpr_classify_endem(rand_test_results)

@@

```{r}
#| label: cpr-rand-comm-parallel-demo
library(future)

@@

```{r}
#| label: acacia-demo
library(future)
library(canaper)

@@

```{r}
#| label: acacia-plot
library(patchwork) # for multipart-panels
library(tidyverse) # includes ggplot2, other packages for data tidying

@@

The color palette used above has been provided in the package as `cpr_endem_cols`, and was selected to be distinguishable regardless of color vision type.
We recommend using this color palette for maximum accessibility.

@@

The `canaper` package enables CANAPE completely within R for the first time.
This will greatly simplify workflows and facilitate reproducibility for researchers studying spatial biodiversity with R.
Furthermore, `canaper` features efficient computing routines and simple yet flexible implementation of parallel computing, thereby decreasing computation time.
